Improving credibility and efficiency of decision-making within democratic communities via a statistical quorum

### 2018-04-19 statistical-quorum.tex

PeerMind source code is available under open source licence at \url{http://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{http://redacted.for.blind.review}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/peermind.png}
\caption{User interface of PeerMind web application. One can see three column structure, with commenting
section on the left, summary points in the middle, and proposed proposals with voting on the right.}
\label{fig:peer-mind}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/ballot.png}
\caption{Ballot used for voting in PeerMind web application. Users can chose a value between -1 and 1 on a slider,
where -1 means opposition, 1 means in favor, and 0 indifference. They can also chose abstention (they
remove themselves from the population of the community for the vote in question), or to not vote (default), which
means that their vote does not contribute to the quorum.}
\label{fig:ballot}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/results.png}
\caption{Results of a vote in PeerMind web application. Results are shown as an average score through time of the vote.
A user can hover over the chart to see details at that time. Users can see these results in real time during voting.}
\label{fig:results}
\end{figure}

>>>>

PeerMind source code is available under open source licence at \url{https://redacted.for.blind.review} and
anonymized dataset of interactions with the app, including votes, is available at \url{https://redacted.for.blind.review}.

\begin{figure}[ht]
\centering
\includegraphics[width=0.9\textwidth]{figures/peermind.png}
\caption{User interface of PeerMind web application. One can see three column structure, with commenting
section on the left, summary points in the middle, and proposed proposals with voting on the right.}
\label{fig:peer-mind}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/ballot.png}
\caption{Ballot used for voting in PeerMind web application. Users can chose a value between -1 and 1 on a slider,
where -1 means opposition, 1 means in favor, and 0 indifference. They can also chose abstention (they
remove themselves from the population of the community for voting in question), or to not vote (default), which
means that their vote does not contribute to the quorum.}
\label{fig:ballot}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=0.6\textwidth]{figures/results.png}
\caption{Results of a vote in PeerMind web application. Results are shown as an average score through time of voting.
A user can hover over the chart to see details at that time. Users can see these results in real time during voting.}
\label{fig:results}
\end{figure}
